\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-12-04 write_up/cricket.tex
renamed to add grounds + added grounds to match

In cricket matches, three results are possible -- a draw, a win, or a loss. We look at draws -- a common outcome in matches in which overs aren't limited -- later on. For now, we focus on winning and losing. We elide over differential number of draws across formats, estimating the difference in probability of winning and losing.

\section*{Results}
A caveat about interpretation before we report the results. As we discuss in the introduction, we cannot estimate the actual advantage of winning a toss. We can only estimate the net observed advantage, which is the extent to which the teams capitalize on the potential advantage.

The team that wins the toss wins the match 2.3\% more often than it loses it. This is a reasonable sized advantage -- though likely much smaller than the number that most commentators carry in their heads -- in a competitive sport. This advantage, however, is highly variable by format, by conditions, by whether or not a particular formula was used to adjust scores when it rained, and how much better the team that won the toss is vis-\`{a}-vis the competing team. Some of the variability is expected, but as we will see, expectations are often dashed.

>>>>

\section*{Analyses and Results}

We assume that the outcome of a toss is random. Conditional on the outcome of a toss being random, the effect of winning a toss can be attributed to the toss itself. We begin by assessing the validity of the assumption. In particular, we assess whether teams win more tosses in their home country than outside.

In cricket matches, three results are possible: a draw, a win, and a loss. We look at draws, a common outcome in matches in which overs aren't limited, later on. For now, we focus on winning and losing. We elide over differential number of draws across formats, estimating the difference in probability of winning and losing.

A caveat about interpretation before we report the results. As we discuss in the introduction, we cannot estimate the actual advantage of winning a toss. We can only estimate the net observed advantage, which is the extent to which the teams capitalize on the potential advantage.

The team that wins the toss wins the match 2.3\% more often than it loses it. This is a reasonable sized advantage in a competitive sport --- though likely much smaller than the number that most commentators carry in their heads. This advantage, however, is highly variable by format, by conditions, by whether or not a particular formula was used to adjust scores when it rains, and how much better the team that won the toss is vis-\`{a}-vis the competing team. Some of the variability is expected, but as we will see, expectations are often dashed.
